Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-14 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
Formatted for JPCB with slight mods to intro

\documentclass[aps,pre,preprint,groupedaddress,longbibliography]{revtex4-2}
\usepackage{CJK}

@@

@@

  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
  with Time Series Modeling}

  \author{Benjamin J. Coscia}
  \author{Michael R. Shirts}

  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}

  \date{\today}

@@

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least (62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\mu$s).  Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
  This results in relatively high uncertainties in observables such as mean
  squared displacement (MSD), preventing reliable long timescale predictions.
  We are in need of a way of studying the collective motion of a much larger
  set of solutes over much longer timescales.

@@

  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this
  study.~\cite{klages_anomalous_2008}

  Three well-known classes of behavior leading to anomalous subdiffusion are
  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
  motion are frequently used alone or in combination to describe single
  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
  is characterized by a distribution of hop lengths and dwell times, where
  trajectories consist of sequential independent random draws from each
  distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous
  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
  dead ends cause anti-correlated
  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

  We treated our system as an FBM process subordinate to a CTRW, or
  subordinated FBM (sFBM) for short. We fit sFBM models in two ways: First, we
  parameterized solute motion using a single set of parameters fit to a
  hypothesized anomalous diffusion (AD) model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's
  radial distance from the closest pore center. This allows us to include
  the different dynamical behavior of solutes previously observed within the
  pore region versus within the monomer tails.

@@

  We determine the degree of success of our modeling approaches in two ways.
  First, if we can closely reproduce solute MSDs measured from MD simulations
  with realizations of our models, then it is likely that the model
  sufficiently captures solute dynamics and can be used in a predictive
  capacity. Even if a model fails to reproduce the MD MSDs, there is value in
  uncovering the cause of the deviation. 
  %BJC9: I modified the following from the commented out version below it in order to be more consistent with what we actually did.
  The second measure of success is based on the qualitative comparison between
  individual realizations of solute trajectories generated by our models and
  those observed from MD simulations. Even if we can reproduce the solute MSDs
  based on realizations of our models, the absence or inappropriate
  reproduction of hopping and trapping behavior may indicate underlying model
  issues. 
  %The second measure of success is by
  %analysis of the parameters defining each model. The parameters themselves
  %should provide clues that help explain solute dynamics in a coherent way. A
  %model that successfully reproduces MD MSDs, but with nonsensical parameters
  %has severely diminished value as it could be a consequence of over-fitting.

@@

  We ran all MD simulations and energy minimizations using GROMACS
  2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
  We performed all post-simulation trajectory analysis using Python scripts
  which are available online at \\
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
  scripts to use for subsequent calculations are summarized in
  Table~\ref{S-table:python_scripts} of the Supplemental Material.

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plot the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supplemental Material in order to justify
  our choice of equilibration times for each solute.

@@

  There are many methods for estimating the Hurst parameter for a time series.
  \cite{clegg_practical_2006} It can be a difficult task because 
  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
  $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supplemental Material). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

  For correlated hops, solute behavior may be described by subordinated
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to
  describe hop correlations because they share the same autocorrelation
  structure.~\cite{tikanmaki_fractional_2010} The autocovariance function for
  FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supplemental Material for numerical
  simulations illustrating this point.

@@

  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
  the Supplemental Material) of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{S-section:flm_correlation} of the Supplemental Material for
  validation of the approach).

@@

  We constructed the state transition probability matrix, $T$, based on
  observed solute trajectories. Using methods described in our previous work,
  we determined each solute's radial location and which, if any, trapping
  mechanisms affected it at each time step, then assigned the observation to a
  specific state according to the definitions in
  Table~\ref{table:states}.~\cite{coscia_chemically_2019} Analogous to the mode
  transition matrix in Section~\ref{method:model_sFBM}, and based on the
  current and previous state observation, we incremented the appropriate entry
  of an $n~\times~n$ count matrix by 1, where $n$ is the number of states. We
  verified the Markovianity of state transitions as described in
  Section~\ref{S-section:markov_validation} of the Supplemental Material.

@@

  To derive an analytical equation describing the passage time distributions,
  one can frame the problem as a pulse of particles instantaneously released at
  the pore inlet ($z=0$) which moves at a constant velocity, $v$, and spreads
  out as it approaches $L$. This spreading is parameterized by an effective
  diffusivity parameter, $D$. This approach gives results equivalent to if we
  had released each particle individually and then analyzed the positions of
  the ensemble of trajectories as a function of time. The analytical expression
  describing the distribution of first passage times
  is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. A derivation of
  Equation~\ref{eqn:passage_times} is given in
  Section~\ref{S-section:fpt_derivation} of the Supplemental Material. We
  calculated the expected value of Equation~\ref{eqn:passage_times} in order to
  get the MFPT.

@@

  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  We observe that in some cases, solute trajectories extracted from our MD
  simulations display non-stationary behavior. We defined the perceived
  equilibration time point for each solute based on the time at which the
  number of solutes inside the pores and tails stabilized
  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
  evidence of non-stationary solute behavior after the perceived equilibration
  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
  the MSD of the solutes calculated using trajectory data from the first and
  second halves of the ``equilibrated" simulation time. Ethylene glycol and
  methanol show considerable differences between the MSDs of the two halves.
  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
  shapes of urea and acetic acid's MSD curves are also very similar (see
  Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).

@@

  Given stationary data, the AD approach is capable of predicting solute MSDs
  measured from MD simulations within or near statistical uncertainty. In
  Figure~\ref{S-fig:train_test} of the Supplemental Material, we parameterized
  the AD models using the first half of the stationary solute equilibrated
  trajectories and then compared the model predictions to the MD MSD of the
  second half of the stationary trajectories. In most cases, the model
  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.

@@

  We observe correlated emissions drawn from L\'evy stable distributions. The
  deviation of the emission distributions from Gaussian behavior is far more
  pronounced than that seen in the hop length distributions of the previous
  section. We therefore did not consider the Gaussian case (see
  Figure~\ref{fig:gaussian_levy_comparison}). The correlation structure
  between hops is consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
  The parameters of the L\'evy stable distributions along with their Hurst
  parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
  in the Supplemental Material, Table~\ref{S-table:msddm_params}).

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{}\label{fig:flux_curves_ad}
  \end{subfigure}
  \caption{(a) The distributions of first passage times generated from the
	  sFBMcut model fit well to Equation~\ref{eqn:passage_times}. We show
	  similar fits for the remaining solutes in
	  Figure~\ref{S-fig:ad_fpt_fits} of the Supplemental Material. (b) The
	  single particle flux measured by the sFBMcut AD model decays with
	  increasing pore length. The rankings of solute fluxes are consistent
	  with the MSDs predicted by each model. We fit the single particle
	  solute flux versus pore length, $L$, to a power law function of the
	  form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
  }\label{fig:flux_curves}
  \end{figure}

@@

  \section*{Supplemental Material}

  Detailed explanations and expansions upon the results and procedures
  mentioned in the main text are described in the Supplemental Material. This
  information is available free of charge via the Internet at
  http://pubs.acs.org.

>>>>

\documentclass[journal=jpcbfk,manuscript=article]{achemso}
\usepackage{CJK}

@@

\title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

@@

@@

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\mu$s).  Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
  This results in relatively high uncertainties in observables such as mean
  squared displacement (MSD), preventing reliable long timescale predictions.
  We are in need of a way of studying the collective motion of a much larger
  set of solutes over much longer timescales.

@@

  % BJC: I'd say this is where the intro starts to get technical
%  We constructed our first model by applying the existing rigorous theoretical
%  foundation which describes the motion of particles that exhibit non-Brownian,
%  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
%  introduced by fractional calculus are instrumental to this
%  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
%  normally linear diffusion equation to fractional derivative orders, providing
%  descriptions of a much more diverse set of behavior, including subdiffusion,
%  a type of anomalous diffusion exhibited by solutes in this
%  study.~\cite{klages_anomalous_2008}

  %BJC: replacement to above.
  We constructed our first model in order to characterize the hopping and
  trapping behavior displayed by solutes in our MD simulations. This type 
  of non-Brownian dynamical behavior results in subdiffusive transport which
  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}

  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
  % stole thesis from paragraph below it
  We chose to treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

%  Three well-known classes of behavior leading to anomalous subdiffusion are
%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
%  motion are frequently used alone or in combination to describe single
%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
%  is characterized by a distribution of hop lengths and dwell times, where
%  trajectories consist of sequential independent random draws from each
%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
%  viscoelastic environments where each jump comes from a Gaussian distribution
%  but is anti-correlated to its previous
%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
%  dead ends cause anti-correlated
%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

%  We treated our system as an FBM process subordinate to a CTRW, or
%  subordinated FBM (sFBM) for short. 
  We fit sFBM models in two ways: First, we parameterized solute motion using
  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
  Second, we used a two-state approach by extracting two sets of model parameters
  calculated based on a solute's radial distance from the closest pore center. 
  This allows us to include the different dynamical behavior of solutes previously
  observed within the pore region versus within the monomer tails.

@@

  We determine the degree of success of our modeling approaches in two ways.
  First, if we can closely reproduce solute MSDs measured from MD simulations
  with realizations of our models, then it is likely that the model
  sufficiently captures solute dynamics and can be used in a predictive
  capacity. Even if a model fails to reproduce the MD MSDs, there is value in
  uncovering the cause of the deviation. The second measure of success is based
  on the qualitative comparison between individual realizations of solute 
  trajectories generated by our models and those observed from MD simulations. 
  Even if we can reproduce the solute MSDs based on realizations of our models,
  the absence or inappropriate reproduction of hopping and trapping behavior may
  indicate underlying model issues.

@@

  We ran all MD simulations and energy minimizations using GROMACS
  2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
  We performed all post-simulation trajectory analysis using Python scripts
  which are available online at
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
  scripts to use for subsequent calculations are summarized in
  Table~\ref{S-table:python_scripts} of the Supplemental Material.

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plot the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify
  our choice of equilibration times for each solute.

@@

  There are many methods for estimating the Hurst parameter for a time series.
  \cite{clegg_practical_2006} It can be a difficult task because 
  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
  $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

  For correlated hops, solute behavior may be described by subordinated
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to
  describe hop correlations because they share the same autocorrelation
  structure.~\cite{tikanmaki_fractional_2010} The autocovariance function for
  FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
  simulations illustrating this point.

@@

  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
  the Supporting Information) of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{S-section:flm_correlation} of the Supporting Information for
  validation of the approach).

@@

  We constructed the state transition probability matrix, $T$, based on
  observed solute trajectories. Using methods described in our previous work,
  we determined each solute's radial location and which, if any, trapping
  mechanisms affected it at each time step, then assigned the observation to a
  specific state according to the definitions in
  Table~\ref{table:states}.~\cite{coscia_chemically_2019} Analogous to the mode
  transition matrix in Section~\ref{method:model_sFBM}, and based on the
  current and previous state observation, we incremented the appropriate entry
  of an $n~\times~n$ count matrix by 1, where $n$ is the number of states. We
  verified the Markovianity of state transitions as described in
  Section~\ref{S-section:markov_validation} of the Supporting Information.

@@

  To derive an analytical equation describing the passage time distributions,
  one can frame the problem as a pulse of particles instantaneously released at
  the pore inlet ($z=0$) which moves at a constant velocity, $v$, and spreads
  out as it approaches $L$. This spreading is parameterized by an effective
  diffusivity parameter, $D$. This approach gives results equivalent to if we
  had released each particle individually and then analyzed the positions of
  the ensemble of trajectories as a function of time. The analytical expression
  describing the distribution of first passage times
  is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. A derivation of
  Equation~\ref{eqn:passage_times} is given in
  Section~\ref{S-section:fpt_derivation} of the Supporting Information. We
  calculated the expected value of Equation~\ref{eqn:passage_times} in order to
  get the MFPT.

@@

  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  We observe that in some cases, solute trajectories extracted from our MD
  simulations display non-stationary behavior. We defined the perceived
  equilibration time point for each solute based on the time at which the
  number of solutes inside the pores and tails stabilized
  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
  evidence of non-stationary solute behavior after the perceived equilibration
  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
  the MSD of the solutes calculated using trajectory data from the first and
  second halves of the ``equilibrated" simulation time. Ethylene glycol and
  methanol show considerable differences between the MSDs of the two halves.
  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
  shapes of urea and acetic acid's MSD curves are also very similar (see
  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).

@@

  Given stationary data, the AD approach is capable of predicting solute MSDs
  measured from MD simulations within or near statistical uncertainty. In
  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized
  the AD models using the first half of the stationary solute equilibrated
  trajectories and then compared the model predictions to the MD MSD of the
  second half of the stationary trajectories. In most cases, the model
  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.

@@

  We observe correlated emissions drawn from L\'evy stable distributions. The
  deviation of the emission distributions from Gaussian behavior is far more
  pronounced than that seen in the hop length distributions of the previous
  section. We therefore did not consider the Gaussian case (see
  Figure~\ref{fig:gaussian_levy_comparison}). The correlation structure
  between hops is consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
  The parameters of the L\'evy stable distributions along with their Hurst
  parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
  in the Supporting Information, Table~\ref{S-table:msddm_params}).

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{}\label{fig:flux_curves_ad}
  \end{subfigure}
  \caption{(a) The distributions of first passage times generated from the
	  sFBMcut model fit well to Equation~\ref{eqn:passage_times}. We show
	  similar fits for the remaining solutes in
	  Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The
	  single particle flux measured by the sFBMcut AD model decays with
	  increasing pore length. The rankings of solute fluxes are consistent
	  with the MSDs predicted by each model. We fit the single particle
	  solute flux versus pore length, $L$, to a power law function of the
	  form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
  }\label{fig:flux_curves}
  \end{figure}

@@

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures
  mentioned in the main text are described in the Supporting Information. This
  information is available free of charge via the Internet at
  http://pubs.acs.org.
